### 2013-05-29 inst/examples/adp-intro.Rmd
local edits
updated adp-intro

```{r}
N <- 50000 # iterations
M <- 20 # gridsize 
Tmax <- 5 # Time horizon

@@

V <- matrix(0, M, Tmax) # matrix(rep(chi, Tmax), nrow=M) # 
V[,1] <- chi   # fails to explore if it doesn't have at least some non-zero values

>>>>

```{r}
N <- 5000 # iterations
M <- 20 # gridsize 
Tmax <- 5 # Time horizon

@@

V <- matrix(1, M, Tmax)  # A* strategy
# Fails to explore at matrix(0, M, Tmax)
# consider: # V <- matrix(rep(chi, Tmax), nrow=M) # 
# V[,1] <- chi   # fails to explore if it doesn't have at least some non-zero values
